### 2018-04-19 papers/synth/intro.tex

@@

>>>>

Vesicle Traffic Systems(VTS) are the material transport mechanisms
among the compartments inside the biological cells.\cite{vtsIntro}
%
\ashu{Describe VTS in detail}

@@

%
The labels may not have been fully observed.

Furthermore, it is a matter of debate what properties
the VTSs should have, such as stability, i.e., every
chemical that is leaving a compartment comes back.
